---
title: "Atlanta and #allmalepanels: #isa2016 as it happened on Twitter - Data and Analysis"
author: "Felix Haass"
output: 
  html_document
---



```{r, echo = F, message = F, warning=F}

# Load packages

library(dplyr)
library(lubridate)
library(ggplot2)
library(scales)
library(twitteR)


# load the data
load("isa2016data.rdata")



```

## Descriptive Statistics
I count `r length(unique(isa2016df$screenName))` unique Twitter users writing `r nrow(isa2016df)` tweets about #isa2016. This number of Tweets is in the ballpark of [last year's 8187 tweets](https://bretterblog.wordpress.com/2015/03/04/isa2015-as-it-happened-on-twitter/). (Now, many of those are retweets; the number of original tweets excluding retweets is considerably lower: `r isa2016df %>% filter(isRetweet == F) %>% nrow()`.) 

## Timeline of Tweets

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 11}

dt <- 30

isa2016df$date <- as.POSIXct(strptime(isa2016df$created, "%Y-%m-%d %H:%M:%S", tz="GMT"))
isa2016df <- isa2016df %>% 
  arrange(date)

# fix dates
isa2016df$date <- isa2016df$date - (6*60*60)


minDate <- round(min(isa2016df$date), "hours")
maxDate <- round(max(isa2016df$date), "hours")
dateBreaks <- seq(minDate, maxDate, by = 60 * 60)
dateBreaks <- c(dateBreaks[1] - 60 * 60, dateBreaks)

tweetCount <- hist(isa2016df$date, breaks=dateBreaks, plot=FALSE)                             
binBreaks <- tweetCount$breaks[1:length(tweetCount$breaks)-1]

plotData <- data.frame(dates=dateBreaks[1:length(dateBreaks)-1], tweets=as.numeric(tweetCount$count))

# time <- data.frame(xmin = as.POSIXct("2016-03-26 08:15"), xmax = as.POSIXct("2016-03-26 10:00"), ymin=-Inf, ymax=Inf)
           

time_isa2016 <- ggplot(plotData) +
  geom_bar(aes(x=dates, y=tweets), stat="identity", fill = "black", width = 3600) +
  scale_y_continuous("Number of tweets") +
  scale_x_datetime(date_breaks = "1 day", labels = date_format("%d March")) +
  theme(axis.text.x=element_text(hjust=1.1, angle=45), legend.key=element_blank())  +
  theme_bw() +
  labs(x="", title="#isa2016 Twitter usage over time \n") +
  geom_vline(aes(xintercept = as.numeric(as.POSIXct("2016-03-16 00:00:00 UTC"))), color = "firebrick") +
  geom_vline(aes(xintercept = as.numeric(as.POSIXct("2016-03-17 00:00:00 UTC"))), color = "firebrick") +
  geom_vline(aes(xintercept = as.numeric(as.POSIXct("2016-03-18 00:00:00 UTC"))), color = "firebrick") +
  geom_vline(aes(xintercept = as.numeric(as.POSIXct("2016-03-19 00:00:00 UTC"))), color = "firebrick") +
  geom_vline(aes(xintercept = as.numeric(as.POSIXct("2016-03-20 00:00:00 UTC"))), color = "firebrick") +
  geom_text(label = "Day 1", aes(x = as.POSIXct("2016-03-16 13:00:00 UTC"), y = 300), size = 4) +
  geom_text(label = "Day 2", aes(x = as.POSIXct("2016-03-17 13:00:00 UTC"), y = 300), size = 4) +
  geom_text(label = "Day 3", aes(x = as.POSIXct("2016-03-18 13:00:00 UTC"), y = 300), size = 4) +
  geom_text(label = "Day 4", aes(x = as.POSIXct("2016-03-19 13:00:00 UTC"), y = 300), size = 4) +
  theme(axis.text.x=element_text(size = 8))

print(time_isa2016)

```


## Who tweets most?


```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height= 9, fig.width=6.5}

# 
# # plot twenty busiest tweeps
# df <- isa2016df %>% 
#   group_by(screenName) %>% 
#   summarise(all_tweets = n(),
#             retweets = sum(isRetweet),
#             original_tweets = all_tweets - retweets) %>% 
#   ungroup() %>% 
#   top_n( 20, all_tweets) %>% 
#   gather(tweet_type, number, -screenName) %>% 
#   group_by(tweet_type) %>% 
#   arrange(number)
# 
# 
# setup_twitter_oauth(consumer_key = 'DZ3izDTm26J4mdLuJqK8sQ',
#                     consumer_secret='a02Tx4Yh3yPqT5WuWzG7CfnRSpu9mI7huthJOLmg4')
#  
# 
# # get real names
# for(i in 1:nrow(df)) {
#   df[i, "realname"] <- getUser(df[i, "screenName"])$name  
# }
# 
# # create display
# df$disp_name <- paste0(df$realname, " \n(@", df$screenName, ")")

# save(df, file = "../twitter_user_ranking.rdata")

load("../twitter_user_ranking.rdata")

df <- df %>% 
  ungroup() %>% 
  filter(tweet_type != "all_tweets") %>% 
  mutate(tweet_type = ifelse(tweet_type == "original_tweets", "Original Tweet", "Retweet"))

plot_user_ranking <- ggplot(df, 
                            aes(x=reorder(disp_name, number), # reorder factor in order of most frequent
                                y = number)) + 
  geom_bar(stat = "identity", aes(fill = tweet_type)) + 
  scale_x_discrete(labels = df$disp_name) + 
  coord_flip() +
  scale_fill_brewer(palette = "Set1", 
                    guide = guide_legend(title = "")) + 
  labs(x = "", y = "") +
  theme_bw() +
  theme(axis.text.y=element_text(size = 8),legend.position = "bottom") 
  
print(plot_user_ranking)


```


## Most frequent hashtags

```{r, echo=FALSE, message=FALSE, warning=FALSE}

library(stringr)
library(knitr)

hashtags <- str_extract_all(isa2016df$text, "#\\S+")

hashtags <- unlist(hashtags)

hashtags <- str_replace_all(hashtags, "[[:punct:]]", "")
hashtags <- tolower(hashtags)

hashtags <- str_replace_all(hashtags, "allmalepanels", "allmalepanel")

hashtags <- data.frame(hashtags) %>% 
  group_by(hashtags) %>% 
  summarise(number = n()) %>% 
  ungroup() %>% 
  arrange(desc(number)) %>% 
  filter(hashtags != "isa2016") %>% 
  mutate(rank = 1:nrow(.)) %>% 
  dplyr::select(rank, hashtags, number) %>% 
  top_n(10, number)

kable(hashtags)

```

## Most popular tweets

```{r, echo=FALSE, message=FALSE, warning=FALSE}

most_popular_tweets <- isa2016df %>% 
  filter(isRetweet == FALSE) %>% 
  ungroup() %>% 
  mutate(popularity = retweetCount + favoriteCount) %>% 
  arrange(desc(popularity)) %>% 
  top_n(10, popularity) %>% 
  dplyr::select(text, id, screenName, popularity) %>% 
  mutate(text = gsub("\\n", "", text),
         link_to_tweet = paste0("<a href = https://twitter.com/", screenName, "/status/", id, "> Link </a>"),
         screenName = paste0("<a href = https://twitter.com/", screenName, ">", screenName, "</a>"),
         rank = 1:nrow(.)) %>% 
  rename(tweet_text = text,
         twitter_user = screenName) %>% 
  dplyr::select(rank, tweet_text, twitter_user, link_to_tweet, popularity)

kable(most_popular_tweets)


```
